Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Tables n charts n stuff

We also measured the duration of finding clones by the different clone types. These results are displayed in figure \ref{fig:performance}. Although this data is dependent on the implementation, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Most of the time that the refactoring-oriented clone types take longer is spent resolving symbols (to infer FQIs).

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=1\columnwidth]{img/TypeResults}
  \label{fig:performance}
\end{figure}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations} \label{table:locations}
  \medskip
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

We also measured the duration of finding clones by the different clone types. Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is dependent on the implementation, there is a notable difference between the refactoring-oriented clone types and the literature clone types. Most of the time that the refactoring-oriented clone types take longer is spent resolving symbols (to infer FQIs).

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=1\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations} \label{table:locations}
  \medskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location}   & \textbf{\#} & \textbf{\%} \\ \hline
Method Level        & 19,075 & 58.23            \\ \hline
Class Level        & 12,207 & 37.27            \\ \hline
Constructor Level    & 1,080 & 3.30           \\ \hline
Interface Level   & 247 & 0.75           \\ \hline
Enum Level         & 147 & 0.45            \\ \hline
\end{tabular}
\end{center}
\end{table}
